---
params:
  project_name: BiB_Education_Record
---





# BiB Education Record


School contextual and assessments data from BiB child linked education records.



```{r, include=FALSE}
prj_name <- 'BiB_Education_Record'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```





## Local Authority Education Record Contextual Data {#BiB_Education_Record.edrecs_annual_context}


Data set in long form with contextual information for each academic year a child is at school and data is available. Collected information includes school identifieers, SEN status, free school meals status and 'Gifted and Talented' status. edcont_schoolid provides a unqiue ID for each school; as this is based on UPRN this ID will not be affected by academisation/name changes. edcont_psuedoURN can be used to link to the edrecs_additional_school_info table to obtain school level information  for each child



```{r, include=FALSE}
tab_id <- 'BiB_Education_Record.edrecs_annual_context'
prj_name <- 'BiB_Education_Record'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Additional school level data {#BiB_Education_Record.edrecs_additional_school_info}


Additional school level information for Bradford schools. Can be linked to edrecs_annual_context using pseudoURN. Variables prefixed with "dfe_" are sourced from the Department for Education (downloaded October 2022; https://www.get-information-schools.service.gov.uk/Establishments/Search?SelectedTab=Establishments), whilst those prefixed with "ofsted_" contain results of 2021 Ofsead inspections (dowloaded October 2022; https://assets.publishing.service.gov.uk/government/uploads/system/uploads/attachment_data/file/1064054/State_funded_schools_inspections_and_outcomes_between_1_September_2021_and_31_December_2021.csv/preview; sheet: "Most recent inspection"). <br> Please note, this data has not been processed by BiB beyond any required data linkage. Users are advised to sense check all variables prior to inclusion in any analysis.



```{r, include=FALSE}
tab_id <- 'BiB_Education_Record.edrecs_additional_school_info'
prj_name <- 'BiB_Education_Record'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Early Years Foundation Stage Profile Pre 2013 {#BiB_Education_Record.edrecs_eyfsp_1}


The Early Years Foundation Stage Profile is a teacher-led assessment conducted towards the end of the child's Reception year at school. This version was used up to the end of the 2011/2012 academic year.



```{r, include=FALSE}
tab_id <- 'BiB_Education_Record.edrecs_eyfsp_1'
prj_name <- 'BiB_Education_Record'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Early Years Foundation Stage Profile 2013 Plus {#BiB_Education_Record.edrecs_eyfsp_2}


The Early Years Foundation Stage Profile is a teacher-led assessment conducted towards the end of the child's Reception year at school. This version was used from the start of the 2012/2013 academic year.



```{r, include=FALSE}
tab_id <- 'BiB_Education_Record.edrecs_eyfsp_2'
prj_name <- 'BiB_Education_Record'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Year 1 Phonics Assessment {#BiB_Education_Record.edrecs_y1_phonics}


The Phonics Assessment is a teacher-led assessment of phonics ability. It is usually completed towards the end of Year 1 at school, but it can be re-attempted in Year 2 if the standard is not met.



```{r, include=FALSE}
tab_id <- 'BiB_Education_Record.edrecs_y1_phonics'
prj_name <- 'BiB_Education_Record'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Key Stage 1 Assessment Pre 2016 {#BiB_Education_Record.edrecs_ks1_1}


The Key Stage 1 Assessment is a standardised test conducted under exam condition and set by the Standards and Testing Agency. It is completed towards the end of Year 2 at school. This version was used up to the end of the 2014/2015 academic year.



```{r, include=FALSE}
tab_id <- 'BiB_Education_Record.edrecs_ks1_1'
prj_name <- 'BiB_Education_Record'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Key Stage 1 Assessment 2016 Plus {#BiB_Education_Record.edrecs_ks1_2}


The Key Stage 1 Assessment is a standardised test conducted under exam condition and set by the Standards and Testing Agency. It is completed towards the end of Year 2 at school. This version was used from the start of the 2015/2016 academic year.



```{r, include=FALSE}
tab_id <- 'BiB_Education_Record.edrecs_ks1_2'
prj_name <- 'BiB_Education_Record'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Key Stage 2 Assessment 2018/19 {#BiB_Education_Record.edrecs_ks2}


The Key Stage 2 Assessment is a standardised test conducted under exam condition and set by the Standards and Testing Agency. It is completed towards the end of Year 6 at school.



```{r, include=FALSE}
tab_id <- 'BiB_Education_Record.edrecs_ks2'
prj_name <- 'BiB_Education_Record'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



