---
params:
  project_name: BiB_ALL_IN
---





# BiB ALL IN {#bib_all_in}


```{r echo=FALSE}
dl_types <- c('Table detail', 'Variable detail', 'Variable names')
dl_csvs <- c('
bib_all_in
_tables.csv', '
bib_all_in
_variables_meta.csv', '
bib_all_in
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



The ALL IN study (ALLergy and INfection) dataset contains surveys of BiB mothers when the child was12m and 24m old.



```{r, include=FALSE}
prj_name <- 'BiB_ALL_IN'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_project_tables_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_project_tables.R'}

```





## ALL IN 12m Questionnaire {#bib_all_in_allin12_qs}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_all_in_allin12_qs
_variables_meta.csv', '
bib_all_in_allin12_qs
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



ALL IN 12 month questionnaire - questionnaire - main wide format sections



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin12_qs'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 12m Current Childcare {#bib_all_in_allin12_cc}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_all_in_allin12_cc
_variables_meta.csv', '
bib_all_in_allin12_cc
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



ALL IN 12 month questionnaire - current childcare - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin12_cc'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 12m Child Travel {#bib_all_in_allin12_ct}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_all_in_allin12_ct
_variables_meta.csv', '
bib_all_in_allin12_ct
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



ALL IN 12 month questionnaire - children's travel - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin12_ct'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 12m Doctor Diagnoses {#bib_all_in_allin12_dd}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_all_in_allin12_dd
_variables_meta.csv', '
bib_all_in_allin12_dd
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



ALL IN 12 month questionnaire - doctor diagnoses - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin12_dd'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 12m Extra Immunisations {#bib_all_in_allin12_ei}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_all_in_allin12_ei
_variables_meta.csv', '
bib_all_in_allin12_ei
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



ALL IN 12 month questionnaire - extra immunisations - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin12_ei'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 12m Household {#bib_all_in_allin12_hh}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_all_in_allin12_hh
_variables_meta.csv', '
bib_all_in_allin12_hh
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



ALL IN 12 month questionnaire - household - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin12_hh'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 12m Previous Childcare {#bib_all_in_allin12_pc}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_all_in_allin12_pc
_variables_meta.csv', '
bib_all_in_allin12_pc
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



ALL IN 12 month questionnaire - previous childcare - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin12_pc'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 24m Questionnaire {#bib_all_in_allin24_qs}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_all_in_allin24_qs
_variables_meta.csv', '
bib_all_in_allin24_qs
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



ALL IN 24 month questionnaire - questionnaire -main wide format sections



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin24_qs'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 24m Current Childcare {#bib_all_in_allin24_cc}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_all_in_allin24_cc
_variables_meta.csv', '
bib_all_in_allin24_cc
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



ALL IN 24 month questionnaire - current childcare - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin24_cc'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 24m Child Travel {#bib_all_in_allin24_ct}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_all_in_allin24_ct
_variables_meta.csv', '
bib_all_in_allin24_ct
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



ALL IN 24 month questionnaire - children's travel - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin24_ct'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 24m Doctor Diagnoses {#bib_all_in_allin24_dd}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_all_in_allin24_dd
_variables_meta.csv', '
bib_all_in_allin24_dd
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



ALL IN 24 month questionnaire - doctor diagnoses - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin24_dd'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 24m Extra Immunisations {#bib_all_in_allin24_ei}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_all_in_allin24_ei
_variables_meta.csv', '
bib_all_in_allin24_ei
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



ALL IN 24 month questionnaire - extra immunisations - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin24_ei'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 24m Food Allergy {#bib_all_in_allin24_fa}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_all_in_allin24_fa
_variables_meta.csv', '
bib_all_in_allin24_fa
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



ALL IN 24 month questionnaire - food allergy - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin24_fa'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 24m Household {#bib_all_in_allin24_hh}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_all_in_allin24_hh
_variables_meta.csv', '
bib_all_in_allin24_hh
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



ALL IN 24 month questionnaire - household - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin24_hh'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 24m Previous Childcare {#bib_all_in_allin24_pc}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_all_in_allin24_pc
_variables_meta.csv', '
bib_all_in_allin24_pc
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



ALL IN 24 month questionnaire - previous childcare - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin24_pc'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 24m Treatment Abroad {#bib_all_in_allin24_ta}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_all_in_allin24_ta
_variables_meta.csv', '
bib_all_in_allin24_ta
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



ALL IN 24 month questionnaire - treatment abroad - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin24_ta'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



