---
params:
  project_name: BiB_Congenital_Anomalies
---





# BiB Congenital Anomalies {#bib_congenital_anomalies}


```{r echo=FALSE}
dl_types <- c('Table detail', 'Variable detail', 'Variable names')
dl_csvs <- c('
bib_congenital_anomalies
_tables.csv', '
bib_congenital_anomalies
variables_meta.csv', '
bib_congenital_anomalies
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB child congenital anomalies information linked from congenital anomalies registry and GP records.



```{r, include=FALSE}
prj_name <- 'BiB_Congenital_Anomalies'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_project_tables_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_project_tables.R'}

```





## Yorkshire and Humber Congenital Anomalies Register {#bib_congenital_anomalies_conganom_yhcar}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_congenital_anomalies_conganom_yhcar
_variables_meta.csv', '
bib_congenital_anomalies_conganom_yhcar
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Contains data entered into the Yorkshire and Humber Congenital Anomalies Register database. This source holds long data at child level, one ICD10 code per row. These are the final codes, which are not always the same as those initially notified. Note that not all of these were confirmed post-natally, see variable yhcarlConfirmedPostnatally.



```{r, include=FALSE}
tab_id <- 'BiB_Congenital_Anomalies.conganom_yhcar'
prj_name <- 'BiB_Congenital_Anomalies'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Congenital Anomalies GP record linkage to 5yo {#bib_congenital_anomalies_conganom_gp}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_congenital_anomalies_conganom_gp
_variables_meta.csv', '
bib_congenital_anomalies_conganom_gp
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Congenital anomalies up to 5 years of age, identified in GP records by Bishop et al (doi: 10.1136/bmjpo-2017-000171) following EUROCAT guidelines (https://bit.ly/2SS1gVc). ICD10 codes were mapped to CTV3 prior to extraction from GP records.



```{r, include=FALSE}
tab_id <- 'BiB_Congenital_Anomalies.conganom_gp'
prj_name <- 'BiB_Congenital_Anomalies'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



