---
params:
  project_name: BiB_Biobank
---





# BiB Biobank {#bib_biobank}


```{r echo=FALSE}
dl_types <- c('Table detail', 'Variable detail', 'Variable names')
dl_csvs <- c('
bib_biobank
_tables.csv', '
bib_biobank
_variables_meta.csv', '
bib_biobank
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Biosamples collected for storage in the BiB biobank. Contains details of samples collected and samples currently available for use in studies.



```{r, include=FALSE}
prj_name <- 'BiB_Biobank'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_project_tables_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_project_tables.R'}

```





## BiB biobank current samples {#bib_biobank_current_samples}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_biobank_current_samples
_variables_meta.csv', '
bib_biobank_current_samples
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



A catalogue of current sample availability in the BiB biobank. Includes information about sample types, age at collection and study wave of collection for each person.



```{r, include=FALSE}
tab_id <- 'BiB_Biobank.current_samples'
prj_name <- 'BiB_Biobank'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



