---
params:
  project_name: BiB_ALL_IN
---





# BiB ALL IN


The ALL IN study (ALLergy and INfection) dataset contains surveys of BiB mothers when the child was12m and 24m old.



```{r, include=FALSE}
prj_name <- 'BiB_ALL_IN'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_project_tables_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_project_tables.R'}

```





## ALL IN 12m Questionnaire {#BiB_ALL_IN.allin12_qs}


ALL IN 12 month questionnaire - questionnaire - main wide format sections



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin12_qs'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 12m Current Childcare {#BiB_ALL_IN.allin12_cc}


ALL IN 12 month questionnaire - current childcare - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin12_cc'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 12m Child Travel {#BiB_ALL_IN.allin12_ct}


ALL IN 12 month questionnaire - children's travel - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin12_ct'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 12m Doctor Diagnoses {#BiB_ALL_IN.allin12_dd}


ALL IN 12 month questionnaire - doctor diagnoses - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin12_dd'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 12m Extra Immunisations {#BiB_ALL_IN.allin12_ei}


ALL IN 12 month questionnaire - extra immunisations - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin12_ei'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 12m Household {#BiB_ALL_IN.allin12_hh}


ALL IN 12 month questionnaire - household - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin12_hh'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 12m Previous Childcare {#BiB_ALL_IN.allin12_pc}


ALL IN 12 month questionnaire - previous childcare - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin12_pc'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 24m Questionnaire {#BiB_ALL_IN.allin24_qs}


ALL IN 24 month questionnaire - questionnaire -main wide format sections



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin24_qs'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 24m Current Childcare {#BiB_ALL_IN.allin24_cc}


ALL IN 24 month questionnaire - current childcare - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin24_cc'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 24m Child Travel {#BiB_ALL_IN.allin24_ct}


ALL IN 24 month questionnaire - children's travel - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin24_ct'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 24m Doctor Diagnoses {#BiB_ALL_IN.allin24_dd}


ALL IN 24 month questionnaire - doctor diagnoses - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin24_dd'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 24m Extra Immunisations {#BiB_ALL_IN.allin24_ei}


ALL IN 24 month questionnaire - extra immunisations - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin24_ei'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 24m Food Allergy {#BiB_ALL_IN.allin24_fa}


ALL IN 24 month questionnaire - food allergy - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin24_fa'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 24m Household {#BiB_ALL_IN.allin24_hh}


ALL IN 24 month questionnaire - household - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin24_hh'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 24m Previous Childcare {#BiB_ALL_IN.allin24_pc}


ALL IN 24 month questionnaire - previous childcare - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin24_pc'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ALL IN 24m Treatment Abroad {#BiB_ALL_IN.allin24_ta}


ALL IN 24 month questionnaire - treatment abroad - long format section



```{r, include=FALSE}
tab_id <- 'BiB_ALL_IN.allin24_ta'
prj_name <- 'BiB_ALL_IN'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



