---
params:
  project_name: BiB_CohortInfo
---





# BiB Cohort Information {#bib_cohortinfo}


```{r echo=FALSE}
dl_types <- c('Table detail', 'Variable detail', 'Variable names')
dl_csvs <- c('
bib_cohortinfo
_tables.csv', '
bib_cohortinfo
variables_meta.csv', '
bib_cohortinfo
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Information about BiB cohort participants



```{r, include=FALSE}
prj_name <- 'BiB_CohortInfo'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_project_tables_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_project_tables.R'}

```





## BiB person-level information {#bib_cohortinfo_person_info}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_cohortinfo_person_info
_variables_meta.csv', '
bib_cohortinfo_person_info
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB person-level information, including parent-child and sibling linkage.



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.person_info'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Ethnicity information about BiB cohort participants {#bib_cohortinfo_ethnicity}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_cohortinfo_ethnicity
_variables_meta.csv', '
bib_cohortinfo_ethnicity
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Ethnicity information about BiB cohort participants



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.ethnicity'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB participant related pairs {#bib_cohortinfo_related_pairs}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_cohortinfo_related_pairs
_variables_meta.csv', '
bib_cohortinfo_related_pairs
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Related pairs of BiB participants, e.g. mother-child relationships, child-parent relationships



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.related_pairs'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Person information Child {#bib_cohortinfo_child_info}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_cohortinfo_child_info
_variables_meta.csv', '
bib_cohortinfo_child_info
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Administrative cohort information on Child participants.



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.child_info'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Person information Father {#bib_cohortinfo_father_info}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_cohortinfo_father_info
_variables_meta.csv', '
bib_cohortinfo_father_info
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Administrative cohort information on Father participants.



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.father_info'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Person information Mother {#bib_cohortinfo_mother_info}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_cohortinfo_mother_info
_variables_meta.csv', '
bib_cohortinfo_mother_info
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Administrative cohort information on Mother participants.



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.mother_info'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ID Linkage {#bib_cohortinfo_id_linkage}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_cohortinfo_id_linkage
_variables_meta.csv', '
bib_cohortinfo_id_linkage
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Identifiers for BiB cohort participants



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.id_linkage'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Pregnancy information {#bib_cohortinfo_preg_info}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_cohortinfo_preg_info
_variables_meta.csv', '
bib_cohortinfo_preg_info
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Information from administrative records about the BiB pregnancy



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.preg_info'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB genotyping data linkage {#bib_cohortinfo_genotyping_info}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_cohortinfo_genotyping_info
_variables_meta.csv', '
bib_cohortinfo_genotyping_info
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Information about available genotyping data including links to sample IDs.



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.genotyping_info'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB exome sequencing data linkage {#bib_cohortinfo_exomeseq_info}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_cohortinfo_exomeseq_info
_variables_meta.csv', '
bib_cohortinfo_exomeseq_info
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Information about available exome sequencing data including links to sample IDs.



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.exomeseq_info'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB DNA methylation data linkage {#bib_cohortinfo_dnam_info}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_cohortinfo_dnam_info
_variables_meta.csv', '
bib_cohortinfo_dnam_info
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Information about available DNA methylation data including links to sample IDs.



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.dnam_info'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB DNA methylation control sample IDs {#bib_cohortinfo_dnam_controls}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_cohortinfo_dnam_controls
_variables_meta.csv', '
bib_cohortinfo_dnam_controls
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB DNA methylation control sample IDs



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.dnam_controls'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



