---
params:
  project_name: BiB_Proteomics
---



# BiB Proteomics {#BiB_Proteomics}


Proteomics datasets contain protein expression and associated sample selection and quality control data.



```{r, include=FALSE}
prj_name <- 'BiB_Proteomics'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```
## Next generation sequencing controls {#BiB_Proteomics.ngs_control}


Next generation sequenced proteomics data controls



```{r, include=FALSE}
tab_id <- 'BiB_Proteomics.ngs_control'
prj_name <- 'BiB_Proteomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(tab_display)
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(vars_display)
```



## Next generation sequencing project 1 {#BiB_Proteomics.ngs_project1}


Next generation sequenced proteomics data in White European and Pakistani mothers who also have genotype data



```{r, include=FALSE}
tab_id <- 'BiB_Proteomics.ngs_project1'
prj_name <- 'BiB_Proteomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(tab_display)
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(vars_display)
```



## Next generation sequencing project 2 {#BiB_Proteomics.ngs_project2}


Next generation sequenced proteomics data White British and Pakistani mothers who have genotype and metabolomics data, and specific pregnancy or birth outcomes



```{r, include=FALSE}
tab_id <- 'BiB_Proteomics.ngs_project2'
prj_name <- 'BiB_Proteomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(tab_display)
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(vars_display)
```



## QPCR controls {#BiB_Proteomics.qpcr_control}


QPCR proteomics data controls



```{r, include=FALSE}
tab_id <- 'BiB_Proteomics.qpcr_control'
prj_name <- 'BiB_Proteomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(tab_display)
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(vars_display)
```



## QPCR project 1 {#BiB_Proteomics.qpcr_project1}


QPCR proteomics data in White European and Pakistani mothers who also have genotype data



```{r, include=FALSE}
tab_id <- 'BiB_Proteomics.qpcr_project1'
prj_name <- 'BiB_Proteomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(tab_display)
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(vars_display)
```



## QPCR project 2 {#BiB_Proteomics.qpcr_project2}


QPCR proteomics data White British and Pakistani mothers who have genotype and metabolomics data, and specific pregnancy or birth outcomes



```{r, include=FALSE}
tab_id <- 'BiB_Proteomics.qpcr_project2'
prj_name <- 'BiB_Proteomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(tab_display)
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(vars_display)
```



