---
params:
  project_name: BiB_SDQs
---





# BiB SDQs {#bib_sdqs}


```{r echo=FALSE}
dl_types <- c('Table detail', 'Variable detail', 'Variable names')
dl_csvs <- c('
bib_sdqs
_tables.csv', '
bib_sdqs
variables_meta.csv', '
bib_sdqs
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



The Strength and Difficulties Questionnaires from all projects



```{r, include=FALSE}
prj_name <- 'BiB_SDQs'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_project_tables_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_project_tables.R'}

```





## Strength and Difficulties questionnaire from the BiB1000 survey {#bib_sdqs_bib1000_sdq}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_sdqs_bib1000_sdq
_variables_meta.csv', '
bib_sdqs_bib1000_sdq
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Contains SDQ data for those aged 2-4 years and was completed by the parent of the child



```{r, include=FALSE}
tab_id <- 'BiB_SDQs.BiB1000_sdq'
prj_name <- 'BiB_SDQs'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Strength and Difficulties questionnaire from the COVID phase 1 survey {#bib_sdqs_covid_phase1_sdq}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_sdqs_covid_phase1_sdq
_variables_meta.csv', '
bib_sdqs_covid_phase1_sdq
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Contains SDQ data for those aged 4+  years and was completed by the parent of the child



```{r, include=FALSE}
tab_id <- 'BiB_SDQs.COVID_phase1_sdq'
prj_name <- 'BiB_SDQs'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Strength and Difficulties questionnaire from the COVID phase 2 survey {#bib_sdqs_covid_phase2_sdq}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_sdqs_covid_phase2_sdq
_variables_meta.csv', '
bib_sdqs_covid_phase2_sdq
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Contains SDQ data for those aged 4+  years and was completed by the parent of the child



```{r, include=FALSE}
tab_id <- 'BiB_SDQs.COVID_phase2_sdq'
prj_name <- 'BiB_SDQs'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Strength and Difficulties questionnaire from the COVID phase 3 survey {#bib_sdqs_covid_phase3_sdq}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_sdqs_covid_phase3_sdq
_variables_meta.csv', '
bib_sdqs_covid_phase3_sdq
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Contains SDQ data for those aged 4+  years and was completed by the parent of the child



```{r, include=FALSE}
tab_id <- 'BiB_SDQs.COVID_phase3_sdq'
prj_name <- 'BiB_SDQs'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Strength and Difficulties questionnaire from the Growing Up survey {#bib_sdqs_growingup_sdq}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_sdqs_growingup_sdq
_variables_meta.csv', '
bib_sdqs_growingup_sdq
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Contains SDQ data for those aged 4+  years and was completed by the parent of the child



```{r, include=FALSE}
tab_id <- 'BiB_SDQs.GrowingUp_sdq'
prj_name <- 'BiB_SDQs'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Strength and Difficulties questionnaire from the MeDALL survey {#bib_sdqs_medall_sdq}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_sdqs_medall_sdq
_variables_meta.csv', '
bib_sdqs_medall_sdq
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Contains SDQ data for those aged 4+  years and was completed by the parent of the child



```{r, include=FALSE}
tab_id <- 'BiB_SDQs.MeDALL_sdq'
prj_name <- 'BiB_SDQs'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Strength and Difficulties questionnaire from the Primary School Years surve {#bib_sdqs_primaryschoolyears_sdq}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_sdqs_primaryschoolyears_sdq
_variables_meta.csv', '
bib_sdqs_primaryschoolyears_sdq
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Contains SDQ data for those aged 4+  years and was completed by the teacher of the child



```{r, include=FALSE}
tab_id <- 'BiB_SDQs.PrimarySchoolYears_sdq'
prj_name <- 'BiB_SDQs'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Strength and Difficulties questionnaire from the Starting School survey {#bib_sdqs_startingschool_sdq}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_sdqs_startingschool_sdq
_variables_meta.csv', '
bib_sdqs_startingschool_sdq
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Contains SDQ data for those aged 4+  years and was completed by the teacher of the child



```{r, include=FALSE}
tab_id <- 'BiB_SDQs.StartingSchool_sdq'
prj_name <- 'BiB_SDQs'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



