---
params:
  project_name: BiB_Baseline
---





# BiB Baseline {#bib_baseline}


```{r echo=FALSE}
dl_types <- c('Table detail', 'Variable detail', 'Variable names')
dl_csvs <- c('
bib_baseline
_tables.csv', '
bib_baseline
_variables_meta.csv', '
bib_baseline
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Baseline surveys completed on BiB cohort registration during pregnancy.



```{r, include=FALSE}
prj_name <- 'BiB_Baseline'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_project_tables_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_project_tables.R'}

```





## Mother baseline survey {#bib_baseline_base_m_survey}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_baseline_base_m_survey
_variables_meta.csv', '
bib_baseline_base_m_survey
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Maternal baseline questionnaire. Main table, contains variables collected in all three questionnaire phases.



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_m_survey'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Mother food frequency and knowledge survey questions phase 2 {#bib_baseline_base_m2_foodfrequency}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_baseline_base_m2_foodfrequency
_variables_meta.csv', '
bib_baseline_base_m2_foodfrequency
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



A series of food / diet survey questions from BiB Mothers Baseline survey (phase 2) relating to food frequency and knowledge



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_m2_foodfrequency'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Mother consumption of fats survey questions phase 1 {#bib_baseline_base_m1_consumptionoffats}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_baseline_base_m1_consumptionoffats
_variables_meta.csv', '
bib_baseline_base_m1_consumptionoffats
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



A series of food / diet survey questions from BiB Mothers Baseline survey (phase 1) relating to the consumption of fats



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_m1_consumptionoffats'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Mother cooking methods survey questions phase 1 and phase 2 {#bib_baseline_base_m12_cookingmethods}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_baseline_base_m12_cookingmethods
_variables_meta.csv', '
bib_baseline_base_m12_cookingmethods
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



A series of food / diet survey questions from BiB Mothers Baseline survey (phase 1 and phase 2) relating to cooking methods



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_m12_cookingmethods'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB Baseline mother exercise phase 1 {#bib_baseline_base_m1_exercise}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_baseline_base_m1_exercise
_variables_meta.csv', '
bib_baseline_base_m1_exercise
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



A series of exercise survey questions from BiB Baseline exercise survey phase 1



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_m1_exercise'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB Baseline mother food frequency phase 1 {#bib_baseline_base_m1_foodfrequency}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_baseline_base_m1_foodfrequency
_variables_meta.csv', '
bib_baseline_base_m1_foodfrequency
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



A series of exercise survey questions from BiB Baseline food frequency survey phase 1



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_m1_foodfrequency'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB Baseline mother exercise phase 2 and phase 3 {#bib_baseline_base_m23_exercise}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_baseline_base_m23_exercise
_variables_meta.csv', '
bib_baseline_base_m23_exercise
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



A series of exercise survey questions from BiB Baseline exercise survey phase 2 and phase 3



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_m23_exercise'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Mother baseline phase 1 {#bib_baseline_base_m1_survey}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_baseline_base_m1_survey
_variables_meta.csv', '
bib_baseline_base_m1_survey
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Maternal baseline questionnaire. This source contains data collected only in Phase 1 (of 3 Phases). These items relate to Social Capital.



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_m1_survey'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Father baseline survey {#bib_baseline_base_f_survey}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_baseline_base_f_survey
_variables_meta.csv', '
bib_baseline_base_f_survey
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB father baseline questionnaire, mostly completed at pregnancy recruitment appointment. There were problems with the stored questionnaire date, so date of questionnaire is set to pregnancy recruitment date.



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_f_survey'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Mother baseline phase 2 and 3 {#bib_baseline_base_m23_survey}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_baseline_base_m23_survey
_variables_meta.csv', '
bib_baseline_base_m23_survey
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Maternal baseline questionnaire. Contains variables collected in phases 2 and 3.



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_m23_survey'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



