---
params:
  project_name: BiB_Biosamples
---





# BiB Biosamples {#bib_biosamples}


```{r echo=FALSE}
dl_types <- c('Table detail', 'Variable detail', 'Variable names')
dl_csvs <- c('
bib_biosamples
_tables.csv', '
bib_biosamples
variables_meta.csv', '
bib_biosamples
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Contains all data derived from assays of BiB blood and urine samples. Also contains manifests of samples stored in the biobank.



```{r, include=FALSE}
prj_name <- 'BiB_Biosamples'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_project_tables_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_project_tables.R'}

```





## Biochemistry hospital bloods taken during pregnancy {#bib_biosamples_hosp_biochem}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_biosamples_hosp_biochem
_variables_meta.csv', '
bib_biosamples_hosp_biochem
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Hospital bloods from mother taken during pregnancy. Biochemistry data.



```{r, include=FALSE}
tab_id <- 'BiB_Biosamples.hosp_biochem'
prj_name <- 'BiB_Biosamples'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Haematology hospital bloods taken during pregnancy {#bib_biosamples_hosp_haem}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_biosamples_hosp_haem
_variables_meta.csv', '
bib_biosamples_hosp_haem
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Hospital bloods from mother taken during pregnancy. Haematology data.



```{r, include=FALSE}
tab_id <- 'BiB_Biosamples.hosp_haem'
prj_name <- 'BiB_Biosamples'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## HbA1c hospital bloods taken during pregnancy {#bib_biosamples_hosp_hba1c}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_biosamples_hosp_hba1c
_variables_meta.csv', '
bib_biosamples_hosp_hba1c
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Hospital bloods from mother taken during pregnancy. HbA1c data.



```{r, include=FALSE}
tab_id <- 'BiB_Biosamples.hosp_hba1c'
prj_name <- 'BiB_Biosamples'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Pregnancy blood biomarkers {#bib_biosamples_pregnancy_bloods}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_biosamples_pregnancy_bloods
_variables_meta.csv', '
bib_biosamples_pregnancy_bloods
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Biomarkers taken from baseline maternal bloods for whole cohort



```{r, include=FALSE}
tab_id <- 'BiB_Biosamples.pregnancy_bloods'
prj_name <- 'BiB_Biosamples'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Pregnancy bloods vitamin D {#bib_biosamples_pregnancy_bloods_vitd}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_biosamples_pregnancy_bloods_vitd
_variables_meta.csv', '
bib_biosamples_pregnancy_bloods_vitd
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Extra biomarkers taken from baseline maternal bloods for vitamin D study



```{r, include=FALSE}
tab_id <- 'BiB_Biosamples.pregnancy_bloods_vitd'
prj_name <- 'BiB_Biosamples'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Maternal baseline GTT {#bib_biosamples_pregnancy_gtt}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_biosamples_pregnancy_gtt
_variables_meta.csv', '
bib_biosamples_pregnancy_gtt
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Maternal baseline glucose tolerance test



```{r, include=FALSE}
tab_id <- 'BiB_Biosamples.pregnancy_gtt'
prj_name <- 'BiB_Biosamples'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB Growing Up main blood tests {#bib_biosamples_blood_tests}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_biosamples_blood_tests
_variables_meta.csv', '
bib_biosamples_blood_tests
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB Growing Up main blood tests carried out at Bradford Teaching Hospitals



```{r, include=FALSE}
tab_id <- 'BiB_Biosamples.blood_tests'
prj_name <- 'BiB_Biosamples'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Baby cord blood biomarkers {#bib_biosamples_cord_bloods}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_biosamples_cord_bloods
_variables_meta.csv', '
bib_biosamples_cord_bloods
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Biomarkers taken from baby cord bloods for a subcohort of 2176 between Oct 2008 and Oct 2009.



```{r, include=FALSE}
tab_id <- 'BiB_Biosamples.cord_bloods'
prj_name <- 'BiB_Biosamples'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB COVID19 child covid antibody blood tests {#bib_biosamples_covid_antibody_blood_tests}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_biosamples_covid_antibody_blood_tests
_variables_meta.csv', '
bib_biosamples_covid_antibody_blood_tests
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Results of antibody blood tests taken during COVID19 pandemic



```{r, include=FALSE}
tab_id <- 'BiB_Biosamples.covid_antibody_blood_tests'
prj_name <- 'BiB_Biosamples'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB maternal iodine {#bib_biosamples_maternal_iodine}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_biosamples_maternal_iodine
_variables_meta.csv', '
bib_biosamples_maternal_iodine
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Urine samples were collected at ~26 weeks gestation from 7,060 participants. Urinary iodine was estimated at the Leeds Institute of Cardiovascular and Metabolic Medicine, University of Leeds. For further details refer to the following citation: https://doi.org/10.1111/ppe.12719



```{r, include=FALSE}
tab_id <- 'BiB_Biosamples.maternal_iodine'
prj_name <- 'BiB_Biosamples'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB Growing Up renal study blood tests {#bib_biosamples_renal_blood_tests}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_biosamples_renal_blood_tests
_variables_meta.csv', '
bib_biosamples_renal_blood_tests
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB Growing Up blood tests for participants enrolled in the UK Kidney Research renal study, carried out at Bradford Teaching Hospitals



```{r, include=FALSE}
tab_id <- 'BiB_Biosamples.renal_blood_tests'
prj_name <- 'BiB_Biosamples'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB Growing Up renal study Cystatin C {#bib_biosamples_renal_cystatinc}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_biosamples_renal_cystatinc
_variables_meta.csv', '
bib_biosamples_renal_cystatinc
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Cystatin C analysis for the BiB Growing Up UK Kindey Research renal study. Specs: Cobas 8000 made by Roche Diagnostics calibrated against international
standard ERM DA471/IFCC




```{r, include=FALSE}
tab_id <- 'BiB_Biosamples.renal_cystatinc'
prj_name <- 'BiB_Biosamples'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



