---
params:
  project_name: BiB_Proteomics
---





# BiB Proteomics {#bib_proteomics}


```{r echo=FALSE}
dl_types <- c('Table detail', 'Variable detail', 'Variable names')
dl_csvs <- c('
bib_proteomics
_tables.csv', '
bib_proteomics
variables_meta.csv', '
bib_proteomics
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Proteomics datasets contain protein expression and associated sample selection and quality control data.



```{r, include=FALSE}
prj_name <- 'BiB_Proteomics'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_project_tables_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_project_tables.R'}

```





## Next generation sequencing controls {#bib_proteomics_ngs_control}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_proteomics_ngs_control
_variables_meta.csv', '
bib_proteomics_ngs_control
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Next generation sequenced proteomics data controls



```{r, include=FALSE}
tab_id <- 'BiB_Proteomics.ngs_control'
prj_name <- 'BiB_Proteomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Next generation sequencing project 1 {#bib_proteomics_ngs_project1}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_proteomics_ngs_project1
_variables_meta.csv', '
bib_proteomics_ngs_project1
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Next generation sequenced proteomics data in White European and Pakistani mothers who also have genotype data



```{r, include=FALSE}
tab_id <- 'BiB_Proteomics.ngs_project1'
prj_name <- 'BiB_Proteomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Next generation sequencing project 2 {#bib_proteomics_ngs_project2}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_proteomics_ngs_project2
_variables_meta.csv', '
bib_proteomics_ngs_project2
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Next generation sequenced proteomics data White British and Pakistani mothers who have genotype and metabolomics data, and specific pregnancy or birth outcomes



```{r, include=FALSE}
tab_id <- 'BiB_Proteomics.ngs_project2'
prj_name <- 'BiB_Proteomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## QPCR controls {#bib_proteomics_qpcr_control}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_proteomics_qpcr_control
_variables_meta.csv', '
bib_proteomics_qpcr_control
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



QPCR proteomics data controls



```{r, include=FALSE}
tab_id <- 'BiB_Proteomics.qpcr_control'
prj_name <- 'BiB_Proteomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## QPCR project 1 {#bib_proteomics_qpcr_project1}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_proteomics_qpcr_project1
_variables_meta.csv', '
bib_proteomics_qpcr_project1
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



QPCR proteomics data in White European and Pakistani mothers who also have genotype data



```{r, include=FALSE}
tab_id <- 'BiB_Proteomics.qpcr_project1'
prj_name <- 'BiB_Proteomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## QPCR project 2 {#bib_proteomics_qpcr_project2}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_proteomics_qpcr_project2
_variables_meta.csv', '
bib_proteomics_qpcr_project2
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



QPCR proteomics data White British and Pakistani mothers who have genotype and metabolomics data, and specific pregnancy or birth outcomes



```{r, include=FALSE}
tab_id <- 'BiB_Proteomics.qpcr_project2'
prj_name <- 'BiB_Proteomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



