---
params:
  project_name: BiB_ChildGrowth
---





# BiB Child Growth {#bib_childgrowth}


```{r echo=FALSE}
dl_types <- c('Table detail', 'Variable detail', 'Variable names')
dl_csvs <- c('
bib_childgrowth
_tables.csv', '
bib_childgrowth
variables_meta.csv', '
bib_childgrowth
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB child growth, anthropometry and bioimpedance data from a variety of sources across the lifecourse.



```{r, include=FALSE}
prj_name <- 'BiB_ChildGrowth'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_project_tables_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_project_tables.R'}

```





## Child anthropometry {#bib_childgrowth_anthropometry}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_childgrowth_anthropometry
_variables_meta.csv', '
bib_childgrowth_anthropometry
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Child anthropometry from a variety of sources taken from across the lifecourse



```{r, include=FALSE}
tab_id <- 'BiB_ChildGrowth.anthropometry'
prj_name <- 'BiB_ChildGrowth'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Child growth NCMP data {#bib_childgrowth_growth_ncmp}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_childgrowth_growth_ncmp
_variables_meta.csv', '
bib_childgrowth_growth_ncmp
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Child growth data from the National Child Measurement Programme taken from across the lifecourse



```{r, include=FALSE}
tab_id <- 'BiB_ChildGrowth.growth_NCMP'
prj_name <- 'BiB_ChildGrowth'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Child growth research data {#bib_childgrowth_growth_researchdata}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_childgrowth_growth_researchdata
_variables_meta.csv', '
bib_childgrowth_growth_researchdata
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Child growth data from surveys taken from across the lifecourse



```{r, include=FALSE}
tab_id <- 'BiB_ChildGrowth.growth_ResearchData'
prj_name <- 'BiB_ChildGrowth'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Child growth primary care data {#bib_childgrowth_growth_primarycare}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_childgrowth_growth_primarycare
_variables_meta.csv', '
bib_childgrowth_growth_primarycare
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Child growth data from primary care taken from across the lifecourse



```{r, include=FALSE}
tab_id <- 'BiB_ChildGrowth.growth_PrimaryCare'
prj_name <- 'BiB_ChildGrowth'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Child bioimpedance {#bib_childgrowth_bioimpedance}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_childgrowth_bioimpedance
_variables_meta.csv', '
bib_childgrowth_bioimpedance
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Child bioimpedance measures mostly aged 7-10y



```{r, include=FALSE}
tab_id <- 'BiB_ChildGrowth.bioimpedance'
prj_name <- 'BiB_ChildGrowth'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



