---
params:
  project_name: BiB_1000
---





# BiB 1000 {#bib_1000}


```{r echo=FALSE}
dl_types <- c('Table detail', 'Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000
_tables.csv', '
bib_1000
_variables_meta.csv', '
bib_1000
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Surveys, anthropometry and derived nutritional data from the BiB 1000 subcohort study.



```{r, include=FALSE}
prj_name <- 'BiB_1000'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_project_tables_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_project_tables.R'}

```





## BiB 1000 6m Questionnaire main table {#bib_1000_bib1000_6m_main}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_6m_main
_variables_meta.csv', '
bib_1000_bib1000_6m_main
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 6m questionnaire main table



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_6m_main'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 6m Parent-reported child diagnoses {#bib_1000_bib1000_6m_b6mqb4}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_6m_b6mqb4
_variables_meta.csv', '
bib_1000_bib1000_6m_b6mqb4
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 6m: Parent-reported child medical diagnoses



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_6m_b6mqb4'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 6m People living in household {#bib_1000_bib1000_6m_b6mqe3}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_6m_b6mqe3
_variables_meta.csv', '
bib_1000_bib1000_6m_b6mqe3
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 6m: People living in household



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_6m_b6mqe3'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 12m Questionnaire main table {#bib_1000_bib1000_12m_main}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_12m_main
_variables_meta.csv', '
bib_1000_bib1000_12m_main
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 12m questionnaire main table



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_12m_main'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 12m People living in household {#bib_1000_bib1000_12m_b12qb4}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_12m_b12qb4
_variables_meta.csv', '
bib_1000_bib1000_12m_b12qb4
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 12m: People living in household



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_12m_b12qb4'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 12m Dried baby cereals {#bib_1000_bib1000_12m_b12qf9}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_12m_b12qf9
_variables_meta.csv', '
bib_1000_bib1000_12m_b12qf9
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 12m: Dried baby cereals



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_12m_b12qf9'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 12m Dried meat or fish-based meals {#bib_1000_bib1000_12m_b12f10}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_12m_b12f10
_variables_meta.csv', '
bib_1000_bib1000_12m_b12f10
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 12m: Dried meat or fish-based meals



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_12m_b12f10'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 12m Dried veg, pasta, rice-based meals {#bib_1000_bib1000_12m_b12f11}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_12m_b12f11
_variables_meta.csv', '
bib_1000_bib1000_12m_b12f11
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 12m: Dried vegetable, pasta or rice-based meals



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_12m_b12f11'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 12m Dried desserts {#bib_1000_bib1000_12m_b12f12}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_12m_b12f12
_variables_meta.csv', '
bib_1000_bib1000_12m_b12f12
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 12m: Dried desserts



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_12m_b12f12'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 12m Breakfast meals {#bib_1000_bib1000_12m_b12f14}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_12m_b12f14
_variables_meta.csv', '
bib_1000_bib1000_12m_b12f14
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 12m: Breakfast meals



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_12m_b12f14'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 12m Meat or fish-based meals {#bib_1000_bib1000_12m_b12f15}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_12m_b12f15
_variables_meta.csv', '
bib_1000_bib1000_12m_b12f15
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 12m: Meat or fish-based meals



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_12m_b12f15'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 12m Veg, pasta, rice-based savoury meals {#bib_1000_bib1000_12m_b12f16}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_12m_b12f16
_variables_meta.csv', '
bib_1000_bib1000_12m_b12f16
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 12m: Vegetable, pasta or rice-based savoury meals



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_12m_b12f16'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 12m Milk or cereal-based desserts {#bib_1000_bib1000_12m_b12f17}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_12m_b12f17
_variables_meta.csv', '
bib_1000_bib1000_12m_b12f17
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 12m: Milk or cereal-based desserts



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_12m_b12f17'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 12m Fruit-based desserts {#bib_1000_bib1000_12m_b12f18}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_12m_b12f18
_variables_meta.csv', '
bib_1000_bib1000_12m_b12f18
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 12m: Fruit-based desserts (not pure fruit puree)



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_12m_b12f18'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 12m Pure fruit puree {#bib_1000_bib1000_12m_b12f19}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_12m_b12f19
_variables_meta.csv', '
bib_1000_bib1000_12m_b12f19
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 12m: Pure fruit puree



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_12m_b12f19'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 12m Types of cereals used {#bib_1000_bib1000_12m_b12f26}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_12m_b12f26
_variables_meta.csv', '
bib_1000_bib1000_12m_b12f26
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 12m: Types of cereals used



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_12m_b12f26'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 12m Other types of yoghurt {#bib_1000_bib1000_12m_b12f69}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_12m_b12f69
_variables_meta.csv', '
bib_1000_bib1000_12m_b12f69
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 12m: Other types of yoghurt or fromage frais



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_12m_b12f69'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 12m Other types of blackcurrant squash {#bib_1000_bib1000_12m_b12f92}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_12m_b12f92
_variables_meta.csv', '
bib_1000_bib1000_12m_b12f92
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 12m: Other types of blackcurrant squash



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_12m_b12f92'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 12m f104 {#bib_1000_bib1000_12m_btf104}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_12m_btf104
_variables_meta.csv', '
bib_1000_bib1000_12m_btf104
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 Questionnaire: bib12_f104



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_12m_btf104'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 12 month child nutrients intake {#bib_1000_bib1000_12m_bib12n}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_12m_bib12n
_variables_meta.csv', '
bib_1000_bib1000_12m_bib12n
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 12 month follow-up child nutrients intake. Derived from Food Frequency Questionnaire from lookup tables of composition of foods. Singletons only (twins and triplets excluded).



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_12m_bib12n'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 18m Questionnaire main table {#bib_1000_bib1000_18m_main}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_18m_main
_variables_meta.csv', '
bib_1000_bib1000_18m_main
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 18m questionnaire main table



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_18m_main'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 18m Child care arrangements {#bib_1000_bib1000_18m_b18qb2}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_18m_b18qb2
_variables_meta.csv', '
bib_1000_bib1000_18m_b18qb2
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 18m: Child care arrangements



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_18m_b18qb2'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 18m Parent-reported child diagnoses {#bib_1000_bib1000_18m_b18qc4}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_18m_b18qc4
_variables_meta.csv', '
bib_1000_bib1000_18m_b18qc4
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 18m: Parent-reported child medical diagnoses



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_18m_b18qc4'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 18m Dried baby cereals {#bib_1000_bib1000_18m_b18qe9}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_18m_b18qe9
_variables_meta.csv', '
bib_1000_bib1000_18m_b18qe9
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 18m: Dried baby cereals



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_18m_b18qe9'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 18m Dried veg, pasta, rice-based meals {#bib_1000_bib1000_18m_b18e11}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_18m_b18e11
_variables_meta.csv', '
bib_1000_bib1000_18m_b18e11
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 18m: Dried vegetable, pasta or rice-based meals



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_18m_b18e11'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 18m Dried desserts {#bib_1000_bib1000_18m_b18e12}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_18m_b18e12
_variables_meta.csv', '
bib_1000_bib1000_18m_b18e12
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 18m: Dried desserts



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_18m_b18e12'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 18m Breakfast meals {#bib_1000_bib1000_18m_b18e14}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_18m_b18e14
_variables_meta.csv', '
bib_1000_bib1000_18m_b18e14
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 18m: Breakfast meals



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_18m_b18e14'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 18m Meat or fish-based meals {#bib_1000_bib1000_18m_b18e15}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_18m_b18e15
_variables_meta.csv', '
bib_1000_bib1000_18m_b18e15
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 18m: Meat or fish-based meals



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_18m_b18e15'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 18m Veg, pasta, rice-based savoury meals {#bib_1000_bib1000_18m_b18e16}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_18m_b18e16
_variables_meta.csv', '
bib_1000_bib1000_18m_b18e16
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 18m: Vegetable, pasta or rice-based savoury meals



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_18m_b18e16'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 18m Milk or cereal-based desserts {#bib_1000_bib1000_18m_b18e17}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_18m_b18e17
_variables_meta.csv', '
bib_1000_bib1000_18m_b18e17
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 18m: Milk or cereal-based desserts



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_18m_b18e17'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 18m Fruit-based desserts {#bib_1000_bib1000_18m_b18e18}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_18m_b18e18
_variables_meta.csv', '
bib_1000_bib1000_18m_b18e18
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 18m: Fruit-based desserts (not pure fruit puree)



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_18m_b18e18'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 18m Pure fruit puree {#bib_1000_bib1000_18m_b18e19}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_18m_b18e19
_variables_meta.csv', '
bib_1000_bib1000_18m_b18e19
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 18m: Pure fruit puree



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_18m_b18e19'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 18m Types of cereals used {#bib_1000_bib1000_18m_b18e26}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_18m_b18e26
_variables_meta.csv', '
bib_1000_bib1000_18m_b18e26
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 18m: Types of cereals used



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_18m_b18e26'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 18m Other types of yoghurt {#bib_1000_bib1000_18m_b18e69}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_18m_b18e69
_variables_meta.csv', '
bib_1000_bib1000_18m_b18e69
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 18m: Other types of yoghurt or fromage frais



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_18m_b18e69'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 18m Other types of blackcurrant squash {#bib_1000_bib1000_18m_b18e92}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_18m_b18e92
_variables_meta.csv', '
bib_1000_bib1000_18m_b18e92
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 18m: Other types of blackcurrant squash



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_18m_b18e92'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 18m Other foods and drinks {#bib_1000_bib1000_18m_bee104}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_18m_bee104
_variables_meta.csv', '
bib_1000_bib1000_18m_bee104
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 18m: Other foods and drinks



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_18m_bee104'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 18m Other snacks consumed by parent {#bib_1000_bib1000_18m_b18qh2}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_18m_b18qh2
_variables_meta.csv', '
bib_1000_bib1000_18m_b18qh2
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 18m: Other snacks consumed by parent



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_18m_b18qh2'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 18m Other ready/take-away meals (parent) {#bib_1000_bib1000_18m_b18qh4}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_18m_b18qh4
_variables_meta.csv', '
bib_1000_bib1000_18m_b18qh4
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 18m: Other ready/take-away meals consumed by parent



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_18m_b18qh4'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 18 month child nutrients intake {#bib_1000_bib1000_18m_bib18n}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_18m_bib18n
_variables_meta.csv', '
bib_1000_bib1000_18m_bib18n
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 18 month follow-up child nutrients intake. Derived from Food Frequency Questionnaire from lookup tables of composition of foods. Singletons only (twins and triplets excluded).



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_18m_bib18n'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 24m Questionnaire main table {#bib_1000_bib1000_24m_main}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_24m_main
_variables_meta.csv', '
bib_1000_bib1000_24m_main
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 24m questionnaire main table



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_24m_main'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 36m Questionnaire main table {#bib_1000_bib1000_36m_main}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_36m_main
_variables_meta.csv', '
bib_1000_bib1000_36m_main
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 36m questionnaire main table



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_36m_main'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 36m Other foods consumed by child {#bib_1000_bib1000_36m_b36j17}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_36m_b36j17
_variables_meta.csv', '
bib_1000_bib1000_36m_b36j17
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 36m: Other foods consumed by child



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_36m_b36j17'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 36m Vitamins or multivitamins {#bib_1000_bib1000_36m_b3j19a}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_36m_b3j19a
_variables_meta.csv', '
bib_1000_bib1000_36m_b3j19a
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 36m: Vitamins or multivitamins



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_36m_b3j19a'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 36m Cod liver oil or other oil {#bib_1000_bib1000_36m_b3j19b}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_36m_b3j19b
_variables_meta.csv', '
bib_1000_bib1000_36m_b3j19b
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 36m: Cod liver oil or other oil



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_36m_b3j19b'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 36m Other supplements {#bib_1000_bib1000_36m_b3j19c}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_36m_b3j19c
_variables_meta.csv', '
bib_1000_bib1000_36m_b3j19c
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 36m: Other supplements



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_36m_b3j19c'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB 1000 36m Physical activity clubs (child) {#bib_1000_bib1000_36m_b36qi9}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_1000_bib1000_36m_b36qi9
_variables_meta.csv', '
bib_1000_bib1000_36m_b36qi9
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB 1000 36m: Physical activity clubs attended by child



```{r, include=FALSE}
tab_id <- 'BiB_1000.bib1000_36m_b36qi9'
prj_name <- 'BiB_1000'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



