---
params:
  project_name: BiB_Metabolomics
---





# BiB Metabolomics {#bib_metabolomics}


Nuclear magnetic resonance (NMR) and mass spectrometry (MS) metabolomics on BiB pregnancy, neonatal and infant samples.



```{r, include=FALSE}
prj_name <- 'BiB_Metabolomics'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_project_tables_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_project_tables.R'}

```





## MS metabolomics paired mother samples scaled {#bib_metabolomics_metms_pairm_s}


Mass spectrometry metabolomics (Metabolon) with over 1300 markers from mother pregnancy bloods. Paired neonatal sample data also available. Scaled values.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metms_pairm_s'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## MS metabolomics paired mother samples raw {#bib_metabolomics_metms_pairm_r}


Mass spectrometry metabolomics (Metabolon) with over 1300 markers from mother pregnancy bloods. Paired neonatal sample data also available. Raw values.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metms_pairm_r'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## MS metabolomics paired mother samples header {#bib_metabolomics_metms_pairm_h}


Sample header information (meta data) from mass spectrometry metabolomics (Metabolon) on paired mother samples.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metms_pairm_h'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## MS metabolomics paired mother samples compound metadata {#bib_metabolomics_metms_pairm_c}


Meta data about compounds (markers) from mass spectrometry metabolomics (Metabolon) on paired mother samples.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metms_pairm_c'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## MS metabolomics paired child samples scaled {#bib_metabolomics_metms_pairc_s}


Mass spectrometry metabolomics (Metabolon) with over 1300 markers from neonatal bloods. Paired mother pregnancy sample data also available. Scaled values.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metms_pairc_s'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## MS metabolomics paired child samples raw {#bib_metabolomics_metms_pairc_r}


Mass spectrometry metabolomics (Metabolon) with over 1300 markers from neonatal bloods. Paired mother pregnancy sample data also available. Raw values.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metms_pairc_r'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## MS metabolomics paired child samples header {#bib_metabolomics_metms_pairc_h}


Sample header information (meta data) from mass spectrometry metabolomics (Metabolon) on paired child samples.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metms_pairc_h'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## MS metabolomics paired child samples compound metadata {#bib_metabolomics_metms_pairc_c}


Meta data about compounds (markers) from mass spectrometry metabolomics (Metabolon) on paired child samples.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metms_pairc_c'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## MS metabolomics 2000 mothers scaled {#bib_metabolomics_metms_2k_s}


Mass spectrometry metabolomics (Metabolon) with over 1200 markers from 2000 selected pregnancy samples. Scaled values.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metms_2k_s'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## MS metabolomics 2000 mothers raw {#bib_metabolomics_metms_2k_r}


Mass spectrometry metabolomics (Metabolon) with over 1200 markers from 2000 selected pregnancy samples. Raw values.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metms_2k_r'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## MS metabolomics 2000 mothers header {#bib_metabolomics_metms_2k_h}


Sample header information (meta data) from mass spectrometry metabolomics (Metabolon) on 2000 pregnancy samples.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metms_2k_h'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## MS metabolomics 2000 mothers compound metadata {#bib_metabolomics_metms_2k_c}


Meta data about compounds (markers) from mass spectrometry metabolomics (Metabolon) on 2000 pregnancy samples.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metms_2k_c'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## NMR metabolomics mother data {#bib_metabolomics_metnmr_mother_d}


Nuclear magnetic resonance metabolomics (Nightingale) with 227 markers from mother pregnancy bloods.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metnmr_mother_d'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## NMR metabolomics mother annotations {#bib_metabolomics_metnmr_mother_a}


Compound annotations for nuclear magnetic resonance metabolomics (Nightingale) with 227 markers from mother pregnancy bloods.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metnmr_mother_a'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## NMR metabolomics baby data {#bib_metabolomics_metnmr_baby_d}


Nuclear magnetic resonance metabolomics (Nightingale) with 85 markers from neonatal cord bloods.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metnmr_baby_d'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## NMR metabolomics baby annotations {#bib_metabolomics_metnmr_baby_a}


Compound annotations for nuclear magnetic resonance metabolomics (Nightingale) with 85 markers from neonatal cord bloods.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metnmr_baby_a'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## NMR metabolomics infant 12m data {#bib_metabolomics_metnmr_infant12_d}


Nuclear magnetic resonance metabolomics (Nightingale) with 228 markers from infant bloods collected at the 12m wave.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metnmr_infant12_d'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## NMR metabolomics infant 12m annotations {#bib_metabolomics_metnmr_infant12_a}


Compound annotations for nuclear magnetic resonance metabolomics (Nightingale) with 228 markers from infant bloods collected at the 12m wave.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metnmr_infant12_a'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## NMR metabolomics infant 24m data {#bib_metabolomics_metnmr_infant24_d}


Nuclear magnetic resonance metabolomics (Nightingale) with 228 markers from infant bloods collected at the 24m wave.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metnmr_infant24_d'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## NMR metabolomics infant 24m annotations {#bib_metabolomics_metnmr_infant24_a}


Compound annotations for nuclear magnetic resonance metabolomics (Nightingale) with 228 markers from infant bloods collected at the 24m wave.



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metnmr_infant24_a'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## NMR metabolomics Growing Up child results {#bib_metabolomics_metnmr_gu_child_results}


NMR metabolomics Growing Up child results



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metnmr_gu_child_results'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## NMR metabolomics Growing Up child QC {#bib_metabolomics_metnmr_gu_child_qc}


NMR metabolomics Growing Up child QC



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metnmr_gu_child_qc'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## NMR metabolomics Growing Up mother results {#bib_metabolomics_metnmr_gu_mother_results}


NMR metabolomics Growing Up mother results



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metnmr_gu_mother_results'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## NMR metabolomics Growing Up mother QC {#bib_metabolomics_metnmr_gu_mother_qc}


NMR metabolomics Growing Up mother QC



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metnmr_gu_mother_qc'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## NMR metabolomics Growing Up father results {#bib_metabolomics_metnmr_gu_father_results}


NMR metabolomics Growing Up father results



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metnmr_gu_father_results'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## NMR metabolomics Growing Up father QC {#bib_metabolomics_metnmr_gu_father_qc}


NMR metabolomics Growing Up father QC



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metnmr_gu_father_qc'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## NMR metabolomics Growing Up biomarker annotations {#bib_metabolomics_metnmr_gu_biomarker_annotations}


NMR metabolomics Growing Up biomarker annotations



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metnmr_gu_biomarker_annotations'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## NMR metabolomics Growing Up compound QC tags {#bib_metabolomics_metnmr_gu_qc_tag}


NMR metabolomics Growing Up compound QC tags



```{r, include=FALSE}
tab_id <- 'BiB_Metabolomics.metnmr_gu_qc_tag'
prj_name <- 'BiB_Metabolomics'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



