---
params:
  project_name: BiB_Pregnancy
---





# BiB Pregnancy {#bib_pregnancy}


```{r echo=FALSE}
dl_types <- c('Table detail', 'Variable detail', 'Variable names')
dl_csvs <- c('
bib_pregnancy
_tables.csv', '
bib_pregnancy
variables_meta.csv', '
bib_pregnancy
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Information from maternal and infant health records around the time of the BiB pregnancy and birth.



```{r, include=FALSE}
prj_name <- 'BiB_Pregnancy'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_project_tables_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_project_tables.R'}

```





## Eclipse pregnancy record {#bib_pregnancy_eclipse_preg}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_pregnancy_eclipse_preg
_variables_meta.csv', '
bib_pregnancy_eclipse_preg
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Pregnancy measures from eClipse electronic record and notes backfill.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.eclipse_preg'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Eclipse neonatal record {#bib_pregnancy_eclipse_baby}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_pregnancy_eclipse_baby
_variables_meta.csv', '
bib_pregnancy_eclipse_baby
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Baby measures from eClipse electronic record



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.eclipse_baby'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Maternity records mother info {#bib_pregnancy_matrecs_bib_mum}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_pregnancy_matrecs_bib_mum
_variables_meta.csv', '
bib_pregnancy_matrecs_bib_mum
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Abstraction of routine information from maternal paper records for the Born in Bradford cohort. The abstraction was funded by a NIHR HTA project (11-99-02). Four trained research assistants abstracted data from maternal paper records. The abstraction was conducted in 2013. Only women with completed baseline questionnaires, oral glucose tolerance test results and birth outcomes were eligible. Data were entered straight into a web database. Accuracy of abstractions were checked on 5% of records for all abstracted data, all error rates were less than 1%. This source contains information about the mother derived from this exercise.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_mum'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Maternity records pre-BiB pregnancy {#bib_pregnancy_matrecs_prebib_preg}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_pregnancy_matrecs_prebib_preg
_variables_meta.csv', '
bib_pregnancy_matrecs_prebib_preg
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Abstraction of routine information from maternal paper records for the Born in Bradford cohort. The abstraction was funded by a NIHR HTA project (11-99-02). Four trained research assistants abstracted data from maternal paper records. The abstraction was conducted in 2013. Only women with completed baseline questionnaires, oral glucose tolerance test results and birth outcomes were eligible. Data were entered straight into a web database. Accuracy of abstractions were checked on 5% of records for all abstracted data, all error rates were less than 1%. This source contains information about pregnancies from before the BiB index pregnancy.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_prebib_preg'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Maternity records pre-BiB infant {#bib_pregnancy_matrecs_prebib_inf}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_pregnancy_matrecs_prebib_inf
_variables_meta.csv', '
bib_pregnancy_matrecs_prebib_inf
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Abstraction of routine information from maternal paper records for the Born in Bradford cohort. The abstraction was funded by a NIHR HTA project (11-99-02). Four trained research assistants abstracted data from maternal paper records. The abstraction was conducted in 2013. Only women with completed baseline questionnaires, oral glucose tolerance test results and birth outcomes were eligible. Data were entered straight into a web database. Accuracy of abstractions were checked on 5% of records for all abstracted data, all error rates were less than 1%. This source contains information about infants from before BiB.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_prebib_inf'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Maternity records BiB pregnancy {#bib_pregnancy_matrecs_bib_preg}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_pregnancy_matrecs_bib_preg
_variables_meta.csv', '
bib_pregnancy_matrecs_bib_preg
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Abstraction of routine information from maternal paper records for the Born in Bradford cohort. The abstraction was funded by a NIHR HTA project (11-99-02). Four trained research assistants abstracted data from maternal paper records. The abstraction was conducted in 2013. Only women with completed baseline questionnaires, oral glucose tolerance test results and birth outcomes were eligible. Data were entered straight into a web database. Accuracy of abstractions were checked on 5% of records for all abstracted data, all error rates were less than 1%. This source contains information from the current BiB pregnancy.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_preg'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Maternity records admissions {#bib_pregnancy_matrecs_bib_admiss}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_pregnancy_matrecs_bib_admiss
_variables_meta.csv', '
bib_pregnancy_matrecs_bib_admiss
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



This source contains information about hospital admissions during the maternal period. 80 observations were dropped due to missing data or data entry errors.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_admiss'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Maternity records pregnancy blood pressure {#bib_pregnancy_matrecs_bib_pregbp}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_pregnancy_matrecs_bib_pregbp
_variables_meta.csv', '
bib_pregnancy_matrecs_bib_pregbp
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



This source contains information about blood pressure during the BiB pregnancy. 940 observations were dropped due to data entry errors.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_pregbp'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Maternity records labour blood pressure {#bib_pregnancy_matrecs_bib_labbp}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_pregnancy_matrecs_bib_labbp
_variables_meta.csv', '
bib_pregnancy_matrecs_bib_labbp
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



This source contains information about blood pressure during labour for the BiB pregnancy. 1913 observations were dropped due to data entry errors.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_labbp'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Maternity records post-partum blood pressure {#bib_pregnancy_matrecs_bib_postbp}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_pregnancy_matrecs_bib_postbp
_variables_meta.csv', '
bib_pregnancy_matrecs_bib_postbp
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



This source contains information about blood pressure taken postpartum for the BiB pregnancy. 907 observations were dropped due to data entry errors.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_postbp'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Maternity records medications {#bib_pregnancy_matrecs_bib_meds}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_pregnancy_matrecs_bib_meds
_variables_meta.csv', '
bib_pregnancy_matrecs_bib_meds
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



This source contains information about medications taken during the BiB pregnancy.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_meds'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Maternity records oedema {#bib_pregnancy_matrecs_bib_oedema}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_pregnancy_matrecs_bib_oedema
_variables_meta.csv', '
bib_pregnancy_matrecs_bib_oedema
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



This source contains information about oedema events during the BiB pregnancy. 47 cases were dropped due to data entry errors.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_oedema'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Maternity records proteinuria {#bib_pregnancy_matrecs_bib_proteinuria}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_pregnancy_matrecs_bib_proteinuria
_variables_meta.csv', '
bib_pregnancy_matrecs_bib_proteinuria
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



This source contains information about proteinuria observations during the BiB pregnancy.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_proteinuria'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Maternity records BiB infant {#bib_pregnancy_matrecs_bib_inf}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_pregnancy_matrecs_bib_inf
_variables_meta.csv', '
bib_pregnancy_matrecs_bib_inf
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Abstraction of routine information from maternal paper records for the Born in Bradford cohort. The abstraction was funded by a NIHR HTA project (11-99-02). Four trained research assistants abstracted data from maternal paper records. The abstraction was conducted in 2013. Only women with completed baseline questionnaires, oral glucose tolerance test results and birth outcomes were eligible. Data were entered straight into a web database. Accuracy of abstractions were checked on 5% of records for all abstracted data, all error rates were less than 1%. This source contains information about the BiB infant.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_inf'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Pregnancy ultrasound scan {#bib_pregnancy_pregnancy_ultrasound}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_pregnancy_pregnancy_ultrasound
_variables_meta.csv', '
bib_pregnancy_pregnancy_ultrasound
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Pregnancy ultrasound scan



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.pregnancy_ultrasound'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Fetal renal ultrasound {#bib_pregnancy_fetal_renal}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_pregnancy_fetal_renal
_variables_meta.csv', '
bib_pregnancy_fetal_renal
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Ultrasound scans around 34 weeks gestation to measure fetal kidney dimensions (transverse and anteroposterior diameters, length and circumference) and derived volume. This is a nested cohort within the full BiB cohort. Women were recruited at a routine glucose tolerance test at 26-28 weeks gestation and invited to return for a further fetal ultrasound at 34 weeks gestation.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.fetal_renal'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



