---
params:
  project_name: BiB_CohortInfo
---





# BiB Cohort Information


Information about BiB cohort participants



```{r, include=FALSE}
prj_name <- 'BiB_CohortInfo'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```





## BiB person-level information {#BiB_CohortInfo.person_info}


BiB person-level information, including parent-child and sibling linkage.



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.person_info'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Ethnicity information about BiB cohort participants {#BiB_CohortInfo.ethnicity}


Ethnicity information about BiB cohort participants



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.ethnicity'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB participant related pairs {#BiB_CohortInfo.related_pairs}


Related pairs of BiB participants, e.g. mother-child relationships, child-parent relationships



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.related_pairs'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Person information Child {#BiB_CohortInfo.child_info}


Administrative cohort information on Child participants.



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.child_info'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Person information Father {#BiB_CohortInfo.father_info}


Administrative cohort information on Father participants.



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.father_info'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Person information Mother {#BiB_CohortInfo.mother_info}


Administrative cohort information on Mother participants.



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.mother_info'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## ID Linkage {#BiB_CohortInfo.id_linkage}


Identifiers for BiB cohort participants



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.id_linkage'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Pregnancy information {#BiB_CohortInfo.preg_info}


Information from administrative records about the BiB pregnancy



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.preg_info'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB genotyping data linkage {#BiB_CohortInfo.genotyping_info}


Information about available genotyping data including links to sample IDs.



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.genotyping_info'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB exome sequencing data linkage {#BiB_CohortInfo.exomeseq_info}


Information about available exome sequencing data including links to sample IDs.



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.exomeseq_info'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB DNA methylation data linkage {#BiB_CohortInfo.dnam_info}


Information about available DNA methylation data including links to sample IDs.



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.dnam_info'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB DNA methylation control sample IDs {#BiB_CohortInfo.dnam_controls}


BiB DNA methylation control sample IDs



```{r, include=FALSE}
tab_id <- 'BiB_CohortInfo.dnam_controls'
prj_name <- 'BiB_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



