---
params:
  project_name: BiB_Dental
---





# BiB Dental


Child dental surveys and linked dental records.



```{r, include=FALSE}
prj_name <- 'BiB_Dental'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```





## 5yo Dental Survey


Records from the National Dental Epidemiology Programme for England survey of 5 year-olds, matched to BiB IDs



```{r, include=FALSE}
tab_id <- 'BiB_Dental.dsurvey_5yo'
prj_name <- 'BiB_Dental'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Dental extractions under GA


Data from linked dental records indicating dental extraction procedures under general anaesthetic



```{r, include=FALSE}
tab_id <- 'BiB_Dental.dental_ga'
prj_name <- 'BiB_Dental'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## PLATOON dental study participant data


PLATOON dental study participant data



```{r, include=FALSE}
tab_id <- 'BiB_Dental.plat_person'
prj_name <- 'BiB_Dental'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## PLATOON dental study tooth observations


PLATOON dental study tooth observations



```{r, include=FALSE}
tab_id <- 'BiB_Dental.plat_teeth'
prj_name <- 'BiB_Dental'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## PLATOON dental study orthodontic assessment


PLATOON dental study orthodontic assessment



```{r, include=FALSE}
tab_id <- 'BiB_Dental.plat_ortho'
prj_name <- 'BiB_Dental'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## PLATOON dental study survey


PLATOON dental study survey



```{r, include=FALSE}
tab_id <- 'BiB_Dental.plat_survey'
prj_name <- 'BiB_Dental'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```



