---
params:
  project_name: BiB_ChildGrowth
---





# BiB Child Growth


BiB child growth, anthropometry and bioimpedance data from a variety of sources across the lifecourse.



```{r, include=FALSE}
prj_name <- 'BiB_ChildGrowth'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```





## Child anthropometry


Child anthropometry from a variety of sources taken from across the lifecourse



```{r, include=FALSE}
tab_id <- 'BiB_ChildGrowth.anthropometry'
prj_name <- 'BiB_ChildGrowth'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Child growth NCMP data


Child growth data from the National Child Measurement Programme taken from across the lifecourse



```{r, include=FALSE}
tab_id <- 'BiB_ChildGrowth.growth_NCMP'
prj_name <- 'BiB_ChildGrowth'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Child growth research data


Child growth data from surveys taken from across the lifecourse



```{r, include=FALSE}
tab_id <- 'BiB_ChildGrowth.growth_ResearchData'
prj_name <- 'BiB_ChildGrowth'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Child growth primary care data


Child growth data from primary care taken from across the lifecourse



```{r, include=FALSE}
tab_id <- 'BiB_ChildGrowth.growth_PrimaryCare'
prj_name <- 'BiB_ChildGrowth'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Child bioimpedance


Child bioimpedance measures mostly aged 7-10y



```{r, include=FALSE}
tab_id <- 'BiB_ChildGrowth.bioimpedance'
prj_name <- 'BiB_ChildGrowth'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```



