---
params:
  project_name: BiB_Baseline
---





# BiB Baseline


Baseline surveys completed on BiB cohort registration during pregnancy.



```{r, include=FALSE}
prj_name <- 'BiB_Baseline'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```





## Mother baseline survey


Maternal baseline questionnaire. Main table, contains variables collected in all three questionnaire phases.



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_m_survey'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Mother food frequency and knowledge survey questions phase 2


A series of food / diet survey questions from BiB Mothers Baseline survey (phase 2) relating to food frequency and knowledge



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_m2_foodfrequency'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Mother consumption of fats survey questions phase 1


A series of food / diet survey questions from BiB Mothers Baseline survey (phase 1) relating to the consumption of fats



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_m1_consumptionoffats'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Mother cooking methods survey questions phase 1 and phase 2


A series of food / diet survey questions from BiB Mothers Baseline survey (phase 1 and phase 2) relating to cooking methods



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_m12_cookingmethods'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## BiB Baseline mother exercise phase 1


A series of exercise survey questions from BiB Baseline exercise survey phase 1



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_m1_exercise'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## BiB Baseline mother food frequency phase 1


A series of exercise survey questions from BiB Baseline food frequency survey phase 1



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_m1_foodfrequency'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## BiB Baseline mother exercise phase 2 and phase 3


A series of exercise survey questions from BiB Baseline exercise survey phase 2 and phase 3



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_m23_exercise'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Mother baseline phase 1


Maternal baseline questionnaire. This source contains data collected only in Phase 1 (of 3 Phases). These items relate to Social Capital.



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_m1_survey'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Father baseline survey


BiB father baseline questionnaire, mostly completed at pregnancy recruitment appointment. There were problems with the stored questionnaire date, so date of questionnaire is set to pregnancy recruitment date.



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_f_survey'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Mother baseline phase 2 and 3


Maternal baseline questionnaire. Contains variables collected in phases 2 and 3.



```{r, include=FALSE}
tab_id <- 'BiB_Baseline.base_m23_survey'
prj_name <- 'BiB_Baseline'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```



