---
params:
  project_name: BiB_Pregnancy
---





# BiB Pregnancy


Information from maternal and infant health records around the time of the BiB pregnancy and birth.



```{r, include=FALSE}
prj_name <- 'BiB_Pregnancy'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```





## Eclipse pregnancy record


Pregnancy measures from eClipse electronic record and notes backfill.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.eclipse_preg'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Eclipse neonatal record


Baby measures from eClipse electronic record



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.eclipse_baby'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Maternity records mother info


Abstraction of routine information from maternal paper records for the Born in Bradford cohort. The abstraction was funded by a NIHR HTA project (11-99-02). Four trained research assistants abstracted data from maternal paper records. The abstraction was conducted in 2013. Only women with completed baseline questionnaires, oral glucose tolerance test results and birth outcomes were eligible. Data were entered straight into a web database. Accuracy of abstractions were checked on 5% of records for all abstracted data, all error rates were less than 1%. This source contains information about the mother derived from this exercise.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_mum'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Maternity records pre-BiB pregnancy


Abstraction of routine information from maternal paper records for the Born in Bradford cohort. The abstraction was funded by a NIHR HTA project (11-99-02). Four trained research assistants abstracted data from maternal paper records. The abstraction was conducted in 2013. Only women with completed baseline questionnaires, oral glucose tolerance test results and birth outcomes were eligible. Data were entered straight into a web database. Accuracy of abstractions were checked on 5% of records for all abstracted data, all error rates were less than 1%. This source contains information about pregnancies from before the BiB index pregnancy.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_prebib_preg'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Maternity records pre-BiB infant


Abstraction of routine information from maternal paper records for the Born in Bradford cohort. The abstraction was funded by a NIHR HTA project (11-99-02). Four trained research assistants abstracted data from maternal paper records. The abstraction was conducted in 2013. Only women with completed baseline questionnaires, oral glucose tolerance test results and birth outcomes were eligible. Data were entered straight into a web database. Accuracy of abstractions were checked on 5% of records for all abstracted data, all error rates were less than 1%. This source contains information about infants from before BiB.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_prebib_inf'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Maternity records BiB pregnancy


Abstraction of routine information from maternal paper records for the Born in Bradford cohort. The abstraction was funded by a NIHR HTA project (11-99-02). Four trained research assistants abstracted data from maternal paper records. The abstraction was conducted in 2013. Only women with completed baseline questionnaires, oral glucose tolerance test results and birth outcomes were eligible. Data were entered straight into a web database. Accuracy of abstractions were checked on 5% of records for all abstracted data, all error rates were less than 1%. This source contains information from the current BiB pregnancy.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_preg'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Maternity records admissions


This source contains information about hospital admissions during the maternal period. 80 observations were dropped due to missing data or data entry errors.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_admiss'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Maternity records pregnancy blood pressure


This source contains information about blood pressure during the BiB pregnancy. 940 observations were dropped due to data entry errors.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_pregbp'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Maternity records labour blood pressure


This source contains information about blood pressure during labour for the BiB pregnancy. 1913 observations were dropped due to data entry errors.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_labbp'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Maternity records post-partum blood pressure


This source contains information about blood pressure taken postpartum for the BiB pregnancy. 907 observations were dropped due to data entry errors.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_postbp'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Maternity records medications


This source contains information about medications taken during the BiB pregnancy.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_meds'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Maternity records oedema


This source contains information about oedema events during the BiB pregnancy. 47 cases were dropped due to data entry errors.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_oedema'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Maternity records proteinuria


This source contains information about proteinuria observations during the BiB pregnancy.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_proteinuria'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Maternity records BiB infant


Abstraction of routine information from maternal paper records for the Born in Bradford cohort. The abstraction was funded by a NIHR HTA project (11-99-02). Four trained research assistants abstracted data from maternal paper records. The abstraction was conducted in 2013. Only women with completed baseline questionnaires, oral glucose tolerance test results and birth outcomes were eligible. Data were entered straight into a web database. Accuracy of abstractions were checked on 5% of records for all abstracted data, all error rates were less than 1%. This source contains information about the BiB infant.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.matrecs_bib_inf'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Pregnancy ultrasound scan


Pregnancy ultrasound scan



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.pregnancy_ultrasound'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Fetal renal ultrasound


Ultrasound scans around 34 weeks gestation to measure fetal kidney dimensions (transverse and anteroposterior diameters, length and circumference) and derived volume. This is a nested cohort within the full BiB cohort. Women were recruited at a routine glucose tolerance test at 26-28 weeks gestation and invited to return for a further fetal ultrasound at 34 weeks gestation.



```{r, include=FALSE}
tab_id <- 'BiB_Pregnancy.fetal_renal'
prj_name <- 'BiB_Pregnancy'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```



