---
params:
  project_name: BiB_PrimarySchoolYears
---





# BiB Primary School Years


The BiB Primary School Years follow-up.



```{r, include=FALSE}
prj_name <- 'BiB_PrimarySchoolYears'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```





## Primary School Years child information {#BiB_PrimarySchoolYears.child_info}


This table contains basic information about the Primary School Years children.



```{r, include=FALSE}
tab_id <- 'BiB_PrimarySchoolYears.child_info'
prj_name <- 'BiB_PrimarySchoolYears'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Primary School Years SDQ data {#BiB_PrimarySchoolYears.sdq_data}


Teacher completed Strengths and Difficulties Questionnaire for children in the Primary School Years study.



```{r, include=FALSE}
tab_id <- 'BiB_PrimarySchoolYears.sdq_data'
prj_name <- 'BiB_PrimarySchoolYears'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Primary School Years child quiz {#BiB_PrimarySchoolYears.child_quiz}


This table contains the results of the Child Quiz, also known as the Child Wellbeing Survey.



```{r, include=FALSE}
tab_id <- 'BiB_PrimarySchoolYears.child_quiz'
prj_name <- 'BiB_PrimarySchoolYears'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Primary School Years EF BDR task data {#BiB_PrimarySchoolYears.ef_task_bdr}


Primary School Years Executive Function tasks. This table contains data from the Backward Digit Recall (BDR) task.



```{r, include=FALSE}
tab_id <- 'BiB_PrimarySchoolYears.ef_task_bdr'
prj_name <- 'BiB_PrimarySchoolYears'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Primary School Years EF FDR task data {#BiB_PrimarySchoolYears.ef_task_fdr}


Primary School Years Executive Function tasks. This table contains data from the Forward Digit Recall (FDR) task.



```{r, include=FALSE}
tab_id <- 'BiB_PrimarySchoolYears.ef_task_fdr'
prj_name <- 'BiB_PrimarySchoolYears'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Primary School Years EF Corsi task data {#BiB_PrimarySchoolYears.ef_task_corsi}


Primary School Years Executive Function tasks. This table contains data from the Corsi task.



```{r, include=FALSE}
tab_id <- 'BiB_PrimarySchoolYears.ef_task_corsi'
prj_name <- 'BiB_PrimarySchoolYears'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Primary School Years EF Inhibition task data {#BiB_PrimarySchoolYears.ef_task_inhibition}


Primary School Years Executive Function tasks. This table contains data from the Inhibition task.



```{r, include=FALSE}
tab_id <- 'BiB_PrimarySchoolYears.ef_task_inhibition'
prj_name <- 'BiB_PrimarySchoolYears'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Primary School Years EF PS task data {#BiB_PrimarySchoolYears.ef_task_ps}


Primary School Years Executive Function tasks. This table contains data from the Processing Speed (PS) task.



```{r, include=FALSE}
tab_id <- 'BiB_PrimarySchoolYears.ef_task_ps'
prj_name <- 'BiB_PrimarySchoolYears'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Primary School Years CKAT data {#BiB_PrimarySchoolYears.ckat_data}


Main CKAT dataset from the Primary School Years study age 7-10 yrs



```{r, include=FALSE}
tab_id <- 'BiB_PrimarySchoolYears.ckat_data'
prj_name <- 'BiB_PrimarySchoolYears'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



