---
params:
  project_name: BiB_SDQs
---





# BiB SDQs


The Strength and Difficulties Questionnaires from all projects



```{r, include=FALSE}
prj_name <- 'BiB_SDQs'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```





## Strength and Difficulties questionnaire from the BiB1000 survey


Contains SDQ data for those aged 2-4 years and was completed by the parent of the child



```{r, include=FALSE}
tab_id <- 'BiB_SDQs.BiB1000_sdq'
prj_name <- 'BiB_SDQs'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Strength and Difficulties questionnaire from the COVID phase 1 survey


Contains SDQ data for those aged 4+  years and was completed by the parent of the child



```{r, include=FALSE}
tab_id <- 'BiB_SDQs.COVID_phase1_sdq'
prj_name <- 'BiB_SDQs'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Strength and Difficulties questionnaire from the COVID phase 2 survey


Contains SDQ data for those aged 4+  years and was completed by the parent of the child



```{r, include=FALSE}
tab_id <- 'BiB_SDQs.COVID_phase2_sdq'
prj_name <- 'BiB_SDQs'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Strength and Difficulties questionnaire from the COVID phase 3 survey


Contains SDQ data for those aged 4+  years and was completed by the parent of the child



```{r, include=FALSE}
tab_id <- 'BiB_SDQs.COVID_phase3_sdq'
prj_name <- 'BiB_SDQs'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Strength and Difficulties questionnaire from the Growing Up survey


Contains SDQ data for those aged 4+  years and was completed by the parent of the child



```{r, include=FALSE}
tab_id <- 'BiB_SDQs.GrowingUp_sdq'
prj_name <- 'BiB_SDQs'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Strength and Difficulties questionnaire from the MeDALL survey


Contains SDQ data for those aged 4+  years and was completed by the parent of the child



```{r, include=FALSE}
tab_id <- 'BiB_SDQs.MeDALL_sdq'
prj_name <- 'BiB_SDQs'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Strength and Difficulties questionnaire from the Primary School Years surve


Contains SDQ data for those aged 4+  years and was completed by the teacher of the child



```{r, include=FALSE}
tab_id <- 'BiB_SDQs.PrimarySchoolYears_sdq'
prj_name <- 'BiB_SDQs'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```





## Strength and Difficulties questionnaire from the Starting School survey


Contains SDQ data for those aged 4+  years and was completed by the teacher of the child



```{r, include=FALSE}
tab_id <- 'BiB_SDQs.StartingSchool_sdq'
prj_name <- 'BiB_SDQs'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_table_info.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
source('../R/reactable_vars.R', local = knitr::knit_global())
```



