---
params:
  project_name: BiB_Dental
---





# BiB Dental {#bib_dental}


```{r echo=FALSE}
dl_types <- c('Table detail', 'Variable detail', 'Variable names')
dl_csvs <- c('
bib_dental
_tables.csv', '
bib_dental
_variables_meta.csv', '
bib_dental
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Child dental surveys and linked dental records.



```{r, include=FALSE}
prj_name <- 'BiB_Dental'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_project_tables_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_project_tables.R'}

```





## 5yo Dental Survey {#bib_dental_dsurvey_5yo}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_dental_dsurvey_5yo
_variables_meta.csv', '
bib_dental_dsurvey_5yo
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Records from the National Dental Epidemiology Programme for England survey of 5 year-olds, matched to BiB IDs



```{r, include=FALSE}
tab_id <- 'BiB_Dental.dsurvey_5yo'
prj_name <- 'BiB_Dental'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Dental extractions under GA {#bib_dental_dental_ga}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_dental_dental_ga
_variables_meta.csv', '
bib_dental_dental_ga
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Data from linked dental records indicating dental extraction procedures under general anaesthetic



```{r, include=FALSE}
tab_id <- 'BiB_Dental.dental_ga'
prj_name <- 'BiB_Dental'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## PLATOON dental study participant data {#bib_dental_plat_person}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_dental_plat_person
_variables_meta.csv', '
bib_dental_plat_person
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



PLATOON dental study participant data



```{r, include=FALSE}
tab_id <- 'BiB_Dental.plat_person'
prj_name <- 'BiB_Dental'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## PLATOON dental study tooth observations {#bib_dental_plat_teeth}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_dental_plat_teeth
_variables_meta.csv', '
bib_dental_plat_teeth
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



PLATOON dental study tooth observations



```{r, include=FALSE}
tab_id <- 'BiB_Dental.plat_teeth'
prj_name <- 'BiB_Dental'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## PLATOON dental study orthodontic assessment {#bib_dental_plat_ortho}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_dental_plat_ortho
_variables_meta.csv', '
bib_dental_plat_ortho
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



PLATOON dental study orthodontic assessment



```{r, include=FALSE}
tab_id <- 'BiB_Dental.plat_ortho'
prj_name <- 'BiB_Dental'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## PLATOON dental study survey {#bib_dental_plat_survey}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_dental_plat_survey
_variables_meta.csv', '
bib_dental_plat_survey
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



PLATOON dental study survey



```{r, include=FALSE}
tab_id <- 'BiB_Dental.plat_survey'
prj_name <- 'BiB_Dental'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



