---
params:
  project_name: BiB_GrowingUp
---





# BiB Growing Up {#bib_growingup}


```{r echo=FALSE}
dl_types <- c('Table detail', 'Variable detail', 'Variable names')
dl_csvs <- c('
bib_growingup
_tables.csv', '
bib_growingup
variables_meta.csv', '
bib_growingup
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Research clinics and surveys data from the BiB Growing Up follow-up.



```{r, include=FALSE}
prj_name <- 'BiB_GrowingUp'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_project_tables_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_project_tables.R'}

```





## BiB Growing Up participant pathway {#bib_growingup_participant_pathway}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_growingup_participant_pathway
_variables_meta.csv', '
bib_growingup_participant_pathway
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB Growing Up participant pathway - contacts, recruitment, completions, withdrawals etc



```{r, include=FALSE}
tab_id <- 'BiB_GrowingUp.participant_pathway'
prj_name <- 'BiB_GrowingUp'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB Growing Up adult survey {#bib_growingup_adult_survey}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_growingup_adult_survey
_variables_meta.csv', '
bib_growingup_adult_survey
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB Growing Up adult survey



```{r, include=FALSE}
tab_id <- 'BiB_GrowingUp.adult_survey'
prj_name <- 'BiB_GrowingUp'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB Growing Up adult survey - BiB1000 sample {#bib_growingup_adult_survey_bib1000_sample}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_growingup_adult_survey_bib1000_sample
_variables_meta.csv', '
bib_growingup_adult_survey_bib1000_sample
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB Growing Up adult survey - BiB1000 sample



```{r, include=FALSE}
tab_id <- 'BiB_GrowingUp.adult_survey_BiB1000_sample'
prj_name <- 'BiB_GrowingUp'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB Growing Up adult survey - MeDALL sample {#bib_growingup_adult_survey_medall_sample}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_growingup_adult_survey_medall_sample
_variables_meta.csv', '
bib_growingup_adult_survey_medall_sample
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB Growing Up adult survey - MeDALL sample



```{r, include=FALSE}
tab_id <- 'BiB_GrowingUp.adult_survey_MeDALL_sample'
prj_name <- 'BiB_GrowingUp'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB Growing Up child survey (adult completed) {#bib_growingup_child_survey_adult_comp}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_growingup_child_survey_adult_comp
_variables_meta.csv', '
bib_growingup_child_survey_adult_comp
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB Growing Up child survey, completed by adult



```{r, include=FALSE}
tab_id <- 'BiB_GrowingUp.child_survey_adult_comp'
prj_name <- 'BiB_GrowingUp'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB Growing Up child survey (child completed) {#bib_growingup_child_survey_child_comp}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_growingup_child_survey_child_comp
_variables_meta.csv', '
bib_growingup_child_survey_child_comp
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB Growing Up child survey, completed by child



```{r, include=FALSE}
tab_id <- 'BiB_GrowingUp.child_survey_child_comp'
prj_name <- 'BiB_GrowingUp'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB Growing Up DXA scan (mother) {#bib_growingup_dxa_scan_m}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_growingup_dxa_scan_m
_variables_meta.csv', '
bib_growingup_dxa_scan_m
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



DXA scan on cohort mothers completed during the BiB Growing Up study.



```{r, include=FALSE}
tab_id <- 'BiB_GrowingUp.dxa_scan_m'
prj_name <- 'BiB_GrowingUp'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB Growing Up DXA scan (child) {#bib_growingup_dxa_scan_c}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_growingup_dxa_scan_c
_variables_meta.csv', '
bib_growingup_dxa_scan_c
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



DXA scan on cohort children completed during the BiB Growing Up study.



```{r, include=FALSE}
tab_id <- 'BiB_GrowingUp.dxa_scan_c'
prj_name <- 'BiB_GrowingUp'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB Growing Up DXA scan (father) {#bib_growingup_dxa_scan_f}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_growingup_dxa_scan_f
_variables_meta.csv', '
bib_growingup_dxa_scan_f
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



DXA scan on cohort fathers completed during the BiB Growing Up study.



```{r, include=FALSE}
tab_id <- 'BiB_GrowingUp.dxa_scan_f'
prj_name <- 'BiB_GrowingUp'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB Growing Up child blood pressures {#bib_growingup_blood_pressure}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_growingup_blood_pressure
_variables_meta.csv', '
bib_growingup_blood_pressure
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB Growing Up child blood pressures



```{r, include=FALSE}
tab_id <- 'BiB_GrowingUp.blood_pressure'
prj_name <- 'BiB_GrowingUp'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## BiB Growing Up renal study urine analyses {#bib_growingup_renal_urines}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bib_growingup_renal_urines
_variables_meta.csv', '
bib_growingup_renal_urines
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



BiB Growing Up urine tests for participants enrolled in the UK Kidney Research renal study. Mostly carried out at Bradford Teaching Hospitals, except RBP, which was carried out at Sheffield Teaching Hospitals.



```{r, include=FALSE}
tab_id <- 'BiB_GrowingUp.renal_urines'
prj_name <- 'BiB_GrowingUp'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



