---
params:
  project_name: BiBBS_CohortInfo
---



# BiBBS Cohort Information {#BiBBS_CohortInfo}


Information about BiBBS cohort participants



```{r, include=FALSE}
prj_name <- 'BiBBS_CohortInfo'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```
## Pregnancy recruitment {#BiBBS_CohortInfo.recruitment}


Data describing patient pathway through the recruitment process for all booked pregnancies in the target period. (2019-11-30 datafreeze)



```{r, include=FALSE}
tab_id <- 'BiBBS_CohortInfo.recruitment'
prj_name <- 'BiBBS_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(tab_display)
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(vars_display)
```



## Recruited pregnancy information {#BiBBS_CohortInfo.pregnancy}


Information for administrative and linkage purposes regarding recruited pregnancies (2019-11-30 datafreeze)



```{r, include=FALSE}
tab_id <- 'BiBBS_CohortInfo.pregnancy'
prj_name <- 'BiBBS_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(tab_display)
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(vars_display)
```



## Recruited mother information {#BiBBS_CohortInfo.mother}


Information for administrative and linkage purposes regarding recruited Mother participants (2019-11-30 datafreeze)



```{r, include=FALSE}
tab_id <- 'BiBBS_CohortInfo.mother'
prj_name <- 'BiBBS_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(tab_display)
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(vars_display)
```



## Child information {#BiBBS_CohortInfo.child}


Information for administrative and linkage purposes regarding recruited Child participants (2019-11-30 datafreeze)



```{r, include=FALSE}
tab_id <- 'BiBBS_CohortInfo.child'
prj_name <- 'BiBBS_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(tab_display)
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(vars_display)
```



## Partner information {#BiBBS_CohortInfo.partner}


Information for administrative and linkage purposes regarding recruited Partner participants (2019-11-30 datafreeze)



```{r, include=FALSE}
tab_id <- 'BiBBS_CohortInfo.partner'
prj_name <- 'BiBBS_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(tab_display)
```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE}
reactable(vars_display)
```



