---
params:
  project_name: BiBBS_CohortInfo
---





# BiBBS Cohort Information {#bibbs_cohortinfo}


```{r echo=FALSE}
dl_types <- c('Table detail', 'Variable detail', 'Variable names')
dl_csvs <- c('
bibbs_cohortinfo
_tables.csv', '
bibbs_cohortinfo
_variables_meta.csv', '
bibbs_cohortinfo
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Information about BiBBS cohort participants



```{r, include=FALSE}
prj_name <- 'BiBBS_CohortInfo'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_project_tables_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_project_tables.R'}

```





## Pregnancy recruitment {#bibbs_cohortinfo_recruitment}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bibbs_cohortinfo_recruitment
_variables_meta.csv', '
bibbs_cohortinfo_recruitment
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Data describing patient pathway through the recruitment process for all booked pregnancies in the target period. (2019-11-30 datafreeze)



```{r, include=FALSE}
tab_id <- 'BiBBS_CohortInfo.recruitment'
prj_name <- 'BiBBS_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Recruited pregnancy information {#bibbs_cohortinfo_pregnancy}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bibbs_cohortinfo_pregnancy
_variables_meta.csv', '
bibbs_cohortinfo_pregnancy
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Information for administrative and linkage purposes regarding recruited pregnancies (2019-11-30 datafreeze)



```{r, include=FALSE}
tab_id <- 'BiBBS_CohortInfo.pregnancy'
prj_name <- 'BiBBS_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Recruited mother information {#bibbs_cohortinfo_mother}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bibbs_cohortinfo_mother
_variables_meta.csv', '
bibbs_cohortinfo_mother
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Information for administrative and linkage purposes regarding recruited Mother participants (2019-11-30 datafreeze)



```{r, include=FALSE}
tab_id <- 'BiBBS_CohortInfo.mother'
prj_name <- 'BiBBS_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Child information {#bibbs_cohortinfo_child}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bibbs_cohortinfo_child
_variables_meta.csv', '
bibbs_cohortinfo_child
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Information for administrative and linkage purposes regarding recruited Child participants (2019-11-30 datafreeze)



```{r, include=FALSE}
tab_id <- 'BiBBS_CohortInfo.child'
prj_name <- 'BiBBS_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Partner information {#bibbs_cohortinfo_partner}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
bibbs_cohortinfo_partner
_variables_meta.csv', '
bibbs_cohortinfo_partner
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



Information for administrative and linkage purposes regarding recruited Partner participants (2019-11-30 datafreeze)



```{r, include=FALSE}
tab_id <- 'BiBBS_CohortInfo.partner'
prj_name <- 'BiBBS_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



