---
params:
  project_name: BiBBS_CohortInfo
---





# BiBBS Cohort Information {#bibbs_cohortinfo}


Information about BiBBS cohort participants



```{r, include=FALSE}
prj_name <- 'BiBBS_CohortInfo'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_project_tables_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_project_tables.R'}

```





## Pregnancy recruitment {#bibbs_cohortinfo_recruitment}


Data describing patient pathway through the recruitment process for all booked pregnancies in the target period. (2019-11-30 datafreeze)



```{r, include=FALSE}
tab_id <- 'BiBBS_CohortInfo.recruitment'
prj_name <- 'BiBBS_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Recruited pregnancy information {#bibbs_cohortinfo_pregnancy}


Information for administrative and linkage purposes regarding recruited pregnancies (2019-11-30 datafreeze)



```{r, include=FALSE}
tab_id <- 'BiBBS_CohortInfo.pregnancy'
prj_name <- 'BiBBS_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Recruited mother information {#bibbs_cohortinfo_mother}


Information for administrative and linkage purposes regarding recruited Mother participants (2019-11-30 datafreeze)



```{r, include=FALSE}
tab_id <- 'BiBBS_CohortInfo.mother'
prj_name <- 'BiBBS_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Child information {#bibbs_cohortinfo_child}


Information for administrative and linkage purposes regarding recruited Child participants (2019-11-30 datafreeze)



```{r, include=FALSE}
tab_id <- 'BiBBS_CohortInfo.child'
prj_name <- 'BiBBS_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## Partner information {#bibbs_cohortinfo_partner}


Information for administrative and linkage purposes regarding recruited Partner participants (2019-11-30 datafreeze)



```{r, include=FALSE}
tab_id <- 'BiBBS_CohortInfo.partner'
prj_name <- 'BiBBS_CohortInfo'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



