---
params:
  project_name: COVID19_Survey
---





# COVID19 Surveys {#covid19_survey}


```{r echo=FALSE}
dl_types <- c('Table detail', 'Variable detail', 'Variable names')
dl_csvs <- c('
covid19_survey
_tables.csv', '
covid19_survey
_variables_meta.csv', '
covid19_survey
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



A series of mixed-mode surveys conducted during 2020 COVID-19 national lockdown and in the months that followed.



```{r, include=FALSE}
prj_name <- 'COVID19_Survey'
source('../R/get_all_project_metadata.R', local = knitr::knit_global())
```



```{r, include=FALSE}
source('../R/make_project_tables_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_project_tables.R'}

```





## COVID19 Adult  Survey Phase 1 {#covid19_survey_adult_phase1}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
covid19_survey_adult_phase1
_variables_meta.csv', '
covid19_survey_adult_phase1
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



COVID19 adult-completed survey phase 1. Combines respondents from both the BiB and BiBBS cohorts.



```{r, include=FALSE}
tab_id <- 'COVID19_Survey.adult_phase1'
prj_name <- 'COVID19_Survey'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## COVID19 Adult Survey Phase 2 (BiB) {#covid19_survey_adult_bib_phase2}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
covid19_survey_adult_bib_phase2
_variables_meta.csv', '
covid19_survey_adult_bib_phase2
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



COVID19 adult-completed survey phase 2. Just respondents from the BiB cohort.



```{r, include=FALSE}
tab_id <- 'COVID19_Survey.adult_bib_phase2'
prj_name <- 'COVID19_Survey'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## COVID19 Adult Survey Phase 2 (BiBBS) {#covid19_survey_adult_bibbs_phase2}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
covid19_survey_adult_bibbs_phase2
_variables_meta.csv', '
covid19_survey_adult_bibbs_phase2
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



COVID19 adult-completed survey phase 2. Just respondents from the BiBBS cohort.



```{r, include=FALSE}
tab_id <- 'COVID19_Survey.adult_bibbs_phase2'
prj_name <- 'COVID19_Survey'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## COVID19 Adult Survey Phase 3 (BiB and general public) {#covid19_survey_adult_bibplus_phase3}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
covid19_survey_adult_bibplus_phase3
_variables_meta.csv', '
covid19_survey_adult_bibplus_phase3
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



COVID19 adult-completed survey phase 3. Respondents from the BiB cohort and the general public. This table is constructed from questions 20:50 of the BiB Breathes survey.



```{r, include=FALSE}
tab_id <- 'COVID19_Survey.adult_bibplus_phase3'
prj_name <- 'COVID19_Survey'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## COVID19 Adult Survey Phase 3 (BiBBS) {#covid19_survey_adult_bibbs_phase3}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
covid19_survey_adult_bibbs_phase3
_variables_meta.csv', '
covid19_survey_adult_bibbs_phase3
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



COVID19 adult-completed survey phase 3. Just respondents from the BiBBS cohort.



```{r, include=FALSE}
tab_id <- 'COVID19_Survey.adult_bibbs_phase3'
prj_name <- 'COVID19_Survey'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## COVID19 Child Survey Phase 1 {#covid19_survey_child_phase1_covid}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
covid19_survey_child_phase1_covid
_variables_meta.csv', '
covid19_survey_child_phase1_covid
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



COVID19 child survey. Respondents from the BiB cohort. Phase 1.



```{r, include=FALSE}
tab_id <- 'COVID19_Survey.child_phase1_covid'
prj_name <- 'COVID19_Survey'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## COVID19 Child Survey Phase 2 {#covid19_survey_child_phase2_covid}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
covid19_survey_child_phase2_covid
_variables_meta.csv', '
covid19_survey_child_phase2_covid
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



COVID19 child survey. Respondents from the BiB cohort. Phase 2.



```{r, include=FALSE}
tab_id <- 'COVID19_Survey.child_phase2_covid'
prj_name <- 'COVID19_Survey'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```





## COVID19 Child Survey Phase 3 {#covid19_survey_child_phase3_covid}


```{r echo=FALSE}
dl_types <- c('Variable detail', 'Variable names')
dl_csvs <- c('
covid19_survey_child_phase3_covid
_variables_meta.csv', '
covid19_survey_child_phase3_covid
_variables_names.csv')
make_download_table(dl_types, dl_csvs)
```



COVID19 child survey. Respondents from the BiB cohort. Phase 3.



```{r, include=FALSE}
tab_id <- 'COVID19_Survey.child_phase3_covid'
prj_name <- 'COVID19_Survey'
source('../R/make_table_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_table_info.R'}

```



```{r, include=FALSE}
source('../R/make_var_info_display.R', local = knitr::knit_global())
```



```{r, echo=FALSE, file='../R/reactable_vars.R'}

```



